{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2020-12-13 documents/brillouin_pulse_math.tex
Apparent success?
lipidwrapping

The Euler-Lagrange equation is usually brought up in the case of the Brachistochrone problem, or the Principle of Least Action (see Feynman lectures). In this case, the path through space, endpoints a to b, where space would seem to be replaced with the frequency domain.

@@

>>>>

Pulse energy, rather than peak field, is not obviously the ideal constraint for this problem; however, it is the one most compatible with lagrange multiplier techniques.

The Euler-Lagrange equation is usually brought up in the case of the Brachistochrone problem, or the Principle of Least Action (see Feynman lectures). In this case, the path through space from endpoints a to b is replaced with the whole frequency domain from -$\inf$ to +$\inf$.

@@

As noted by Pozar, the complex conjugate arises from the concept of "adjointness". Franks.

Note the ni in the complex conjugate!

### 2020-12-13 documents/charge.tex
Replicated Z,C's result using functionalDerivative! yay
Apparent success?
lipidwrapping

@@

@@

>>>>

(these values were only taken at a pH of 7. A larger charge imbalance might be found at less neutral pHes. However, any effect would be of little practical use if it does not occur at physiological pH.)

@@

This also agrees roughly with Perilla \cite{Physical2017}

@@

Viral capsids self-assemble; it is energetically favorable to.

### 2020-12-13 documents/viscosity.tex
lipidwrapping

However, if we apply the same arguments to microtubules \cite{Viscous2000}, omega_c = 80 GHz, and Q=11.2. The effects of these exposures should have been

>>>>

However, if we apply the same arguments to microtubules \cite{Viscous2000}, we get omega_c = 80 GHz and Q=11.2. The effects of these exposures should have been noticed in the previous studies, so there is probably something gravely wrong with this analysis.

In the steady-state, producing 1 nN from a charge of 10^5 takes some 60 kV/m.
